\documentclass[12pt]{article}
\usepackage{graphicx}
\begin{document}

\renewcommand{\descriptionlabel}[1]{\hspace{\labelsep}\emph{#1}}

\title{BYLAWS OF \\ NEXT CLIMATE, INC}
\date{}
\maketitle

\noindent
\subsubsection*{ARTICLE I: NAME AND PURPOSE}
\begin{description}
\item[Name:] The name of the corporation shall be Next Climate, Inc. It shall be a
nonprofit organization incorporated under the laws of North Carolina.
\item[Purpose:] Next Climate, Inc is organized exclusively for charitable, scientific
and education purposes. The purpose of this corporation is
\begin{itemize}
\item to support and conduct non-partisan research, education, and
  informational activities to increase public awareness of climate
  change,
\item to facilitate the adoption of energy-saving technologies, and
\item to connect consumers with providers of energy-saving
  technologies that both mitigate climate change and save consumers
  money.
\end{itemize}

\end{description}
\subsubsection*{ARTICLE II: MEMBERSHIP}

\emph{Membership:} Membership shall consist of the board of directors.

\subsubsection*{ARTICLE III: BOARD OF DIRECTORS}
\begin{description}
\item[Board role, size, and compensation:] The board is responsible
for overall policy and direction of the association, and delegates
responsibility of day-to-day operations to the staff and
committees. The board shall have up to 20, but not fewer than 3
members. The board receives no compensation other than reasonable
expenses.

\item[Terms:] All board members shall serve two-year terms, but are
eligible for re-election for up to five consecutive terms.

\item[Meetings and notice:] The board shall meet at least annually, at an
agreed upon time and place. An official board meeting requires that
each board member have email notice at least two weeks in advance.

\item[Board elections:] During the last quarter of each calendar year, the
board of directors shall elect Directors to replace those whose terms
will expire at the end of the fiscal year. This election shall take
place during a regular meeting of the directors, called in accordance
with the provisions of these bylaws.

\item[Election procedures:] New directors shall be elected by a majority
of directors present at such a meeting, provided there is a quorum
present. Directors so elected shall serve a term beginning on the first
day of the next calendar year.

\item[Quorum:] A quorum must be attended by at least forty percent of
board members for business transactions to take place and motions to
pass. Attendance by video conference does count towards the quorum.

\item[Officers and Duties:] There shall be two officers of the board,
  consisting of a chair and treasurer. The board can appoint additional officers and
assign duties as needed. The duties of the officers are

\begin{description}
\item[The chair] shall convene regularly scheduled board meetings,
  shall preside or arrange for other members of the Executive
  Committee to preside at each meeting.
\item[The treasurer] shall make a report at each board meeting. The
  treasurer shall chair the finance committee, assist in the
  preparation of the budget, help develop fundraising plans, and make
  financial information available to board members and the public.
\end{description}

\item[Vacancies:] When a vacancy on the board exists mid-term, the
chair must receive nominations for new members from present board
members one week in advance of a board meeting. These nominations
shall be sent out to board members with the regular board meeting
announcement, to be voted upon at the next board meeting. These
vacancies will be filled only to the end of the particular board
member's term.

\item[Resignation, termination, and absences:] Resignation from the
board must be in writing and received by the chair. A board
members shall be terminated from the board due to excess absences,
more than two unexcused absences from board meetings in a year. A
board member may be removed for other reasons by a three-fourths vote
of the remaining directors.

\item[Special meetings:] Special meetings of the board shall be called
upon the request of the chair, or one-third of the board. Notices of
special meetings shall be sent out by the chair to each board
member at least two weeks in advance.
\end{description}

\subsubsection*{ARTICLE IV: COMMITTEES}

\begin{description}
\item[Committee formation:] The board may create committees as needed,
such as fundraising, housing, public relations, data collection, etc.
The board chair appoints all committee chairs.

\item[Executive Committee:] The board officers serve as the members of
the Executive Committee. Except for the power to amend the articles of
incorporation and bylaws, the Executive Committee shall have all the
powers and authority of the board of directors in the intervals
between meetings of the board of directors, and is subject to the
direction and control of the full board.

\end{description}

\subsubsection*{ARTICLE V: EXECUTIVE OFFICERS AND STAFF}
\begin{description}
\item[Chief Executive Officer:] The chief executive officer is hired
by the board.  The chief executive officer has day-to-day
responsibilities for the organization, including carrying out the
organization's goals and policies. The chief executive officer may
appoint or remove any staff or consultants for the Corporation and
establish the rate of compensation for any such staff person or
consultant. The chief executive officer will attend all board
meetings, report on the progress of the organization, answer questions
of the board members and carry out the duties described in the job
description. The board can designate other duties as necessary.
\end{description}

\subsubsection*{ARTICLE VI: AMENDMENTS}
\begin{description}
\item[Amendments:] These bylaws may be amended when necessary by
two-thirds majority of the board of directors. Proposed amendments
must be submitted to the secretary to be sent out with regular board
announcements.
\end{description}

\subsubsection*{CERTIFICATION}

These bylaws were approved at a meeting of the board of directors by a
two-thirds majority vote on March 23, 2012.\\

\vspace{1cm}
\noindent
\line(1,0){250}\\
Robert W. Pinder, Chair

\end{document}